%-------------------------
% Resume in LaTeX — Pradeep Guled
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}

% Tight margins for one page
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\evensidemargin}{-0.45in}
\addtolength{\textwidth}{0.9in}
\addtolength{\topmargin}{-0.55in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\multicolsep}{2pt}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-4pt}]

% Job heading: company + date on line 1, title + location on line 2
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small #3} & \textcolor{gray}{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-1pt}}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=4pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=1pt,itemsep=0pt,parsep=1pt,leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{4pt}}

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{center}
  {\LARGE \textbf{Pradeep Guled}} \\[4pt]
  \small
  Bengaluru, India \;|\;
  \href{mailto:pradeepguled281@gmail.com}{pradeepguled281@gmail.com} \;|\;
  +91-8861944220 \;|\;
  \href{https://github.com/Pradeepguled/}{\faGithub\ GitHub} \;|\;
  \href{https://www.linkedin.com/in/pradeep-guled}{\faLinkedin\ LinkedIn}
\end{center}

\vspace{-6pt}

%-----------SUMMARY-----------------
\section{Summary}
\small{Data Engineer with 4+ years of experience building batch and streaming data platforms on AWS across regulated, data-intensive industries -- including a near real-time Kafka-based alerting and event-triggering platform for healthcare telemetry, and a full-scale Hadoop/Hive to Snowflake \& AWS migration powering batch analytics pipelines. Specialized in Python, SQL, Spark, Snowflake, AWS, and dimensional modeling for large-scale analytics -- with domain experience in complex transactions, compliance-sensitive data, and multi-stakeholder reporting pipelines. Hands-on with GenAI pipelines and vector DBs. Proven collaborator delivering cost-effective, scalable data solutions.}

\vspace{2pt}

%-----------SKILLS (two columns)-----------------
\section{Skills}
\begin{multicols}{2}
\small{
\textbf{Languages:} Python, SQL, SparkSQL \\[1pt]
\textbf{Distributed Processing:} Spark, PySpark, Hadoop, Hive \\[1pt]
\textbf{Streaming \& Messaging:} Kafka, AWS Kinesis \\[1pt]
\textbf{Orchestration:} Airflow, AWS Step Functions \\[1pt]
\textbf{AWS Services:} S3, Glue, EMR, Lambda, Lake Formation

\columnbreak

\textbf{Data Warehousing:} Snowflake, Dimensional Modeling, ETL/ELT \\[1pt]
\textbf{NoSQL \& Storage:} DynamoDB, S3 Object Storage \\[1pt]
\textbf{Data Architecture:} Data Lake, Lakehouse, Distributed Systems \\[1pt]
\textbf{DevOps:} Git, Docker, Linux, CI/CD \\[1pt]
\textbf{ML \& GenAI:} Embeddings, Vector DBs, Semantic Search
}
\end{multicols}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Carelon Global Solutions (Elevance Health)}{12-12-2024 -- Present}
  {Software Engineer II -- Data Engineer}{Bengaluru, India}
\resumeItemListStart
  \resumeItem{Led end-to-end migration of Hadoop/Hive ecosystem to Snowflake and AWS (Glue, S3, Spark) -- involved in architecture design, pipeline development, and production maintenance for the new environment, cutting query latency and enabling elastic scaling.}
  \resumeItem{Owned end-to-end ETL pipelines using AWS Glue, Lambda, Step Functions, and Snowflake, improving data freshness by 30--40\% and reducing compute costs by up to 20\% through warehouse sizing and workload tuning.}
  \resumeItem{Designed dimensional data models (fact/dimension tables) for healthcare cost and claims analytics, handling SCDs and enabling reliable downstream reporting -- identified gaps in existing data structures and drove schema changes adopted across reporting teams.}
  \resumeItem{Optimized PySpark and Snowflake workloads via partitioning and shuffle tuning, reducing pipeline runtimes by 20--30\%.}
  \resumeItem{Led GenAI initiatives -- sourced and integrated new data into vector DB pipelines for embeddings and semantic search, expanding the platform to support new AI consumers.}
  \resumeItem{Collaborated with analytics, architecture, and product teams; presented pipeline designs and cost trade-offs to technical and business stakeholders.}
\resumeItemListEnd

\resumeSubheading
  {Glassbeam India Pvt. Ltd.}{01-02-2022 -- 30-11-2024}
  {Software Engineer -- Data Engineer}{Bengaluru, India}
\resumeItemListStart
  \resumeItem{Maintained and enhanced Kafka-based streaming pipelines for near real-time alerting on healthcare machine telemetry -- designed topic partitioning, consumer group scaling, and offset management for fault-tolerant, low-latency alert delivery.}
  \resumeItem{Maintained large-scale batch ingestion pipelines using PySpark, AWS Glue, Lambda, and S3, onboarding new telemetry data sources into the analytics platform.}
  \resumeItem{Implemented data quality automation and observability across batch and streaming pipelines, cutting manual QA effort by \textasciitilde80\% and improving stability via proactive root cause analysis.}
  \resumeItem{Partnered with analysts and stakeholders to understand data requirements and evolve data structures accordingly.}
\resumeItemListEnd

\resumeSubheading
  {Glassbeam India Pvt. Ltd.}
  {Associate Software Engineer}{Bengaluru, India}{Feb 2022 -- Apr 2023}
\resumeItemListStart
  \resumeItem{Developed Python-based ETL workflow modules for medical device log data, ensuring SLA-driven delivery and collaborating with senior engineers on data quality.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Basaweshwara Engineering College}{2017 -- 2021}
    {B.E. in Computer \& Information Sciences}{Bagalkot, India}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\begin{itemize}[topsep=1pt,itemsep=1pt,parsep=0pt,leftmargin=*]
  \item\small{AWS Certified Data Engineer -- Associate (2025)}
  \item\small{Snowflake SnowPro Core \& Platform Certification (2025)}
  \item\small{Oracle Cloud Infrastructure Generative AI Professional (2025)}
\end{itemize}

\end{document}